\section{Free games / the community}
\subsection{Contribute}
This game is brought to you by the UFO:AI Development team and its countless contributors. All of them share at least one thought: to make UFO:AI a great \underline{free} game. Besides detailed legal implications, mentioned in the following section and given in the appendix, most of all this means that every piece of code used to create this game is publicly available. Even more: you are free -- even wanted -- to change anything you want by yourself whenever you feel you can help make UFO:AI a better way to waste time. This may be typos or even complete mods or patches -- it's up to you.

Since UFO:AI is open-source development by a bunch of non-profit oriented people, this means that there is no backing by a big company in order to pay for extensive testing or balancing. Whenever you encounter a bug, a hardware incompatibility or any other problem, it would be a nice gesture to give something back to the community -- even a carefully filled out bug report \footnote{\url{http://sourceforge.net/tracker/?atid=805242&group_id=157793&func=browse}} helps a lot. So we hope to do our little share to promote free software and build up a productive open-source gaming community. And no matter what kind of skills you call your own, if you are a coder, 2D or 3D artist, map-designer, or even film-script writer, musician, concept-art designer (all of these made UFO:AI what it is today) be assured that there is a project waiting for your help.

If you are interested in adding to the game, please visit the \textit{Contribute} section in our wiki at \ufohomepage. You will find a lot of useful information about model and image formats, a lot of tutorials about mapping, and so on.

\subsection{Contact / Support}
Support, additional information, FAQs and the forum can be found at \ufohomepage.
For a release history, latest releases and bugfixes as well as the bug- and feature-tracker\footnote{\url{http://sourceforge.net/tracker/?group_id=157793}} please see our project page at \url{http://www.sourceforge.org}. Sourceforge also allows you to take a look at our project page, where you find detailed status reports and contribution- and member-lists. In addition to the forum we also host the channel \texttt{ufo:ai} on the freenode\footnote{irc.freenode.org} IRC network. Please make sure you try to find solutions for rather trivial problems on your own before asking on the board or on IRC.  (This is known as \emph{netiquette}.)

For interested media we also provide screenshots and offer further support for any planned coverage -- feel free to contact us.
