\section{First steps}
This chapter is obviously dedicated to players that are new to the UFO-series or maybe even turn based tactical combat games in general. Experienced players may skip this chapter, but of course there is no harm in reading it anyway.

The usual process after starting a new campaign is quite unified and all the same for all kind of players at all levels. First you must choose a proper place for your home base. Even if there are strategic differences between certain locations, there is hardly any no-no spot, so make your selection as you like.

After you have set up your base, you may want to prepare your squad so everything is ready in case aliens immediately show up. In the following we will assume that you start you game with default settings (starting with buildings in base and employees hired). So the next thing you should do is to open up your base-screen (as discussed in the previous chapters) 
% Huh?  There aren't any previous chapters.  Subsequent ones maybe?  Or else ditch this line.
$\rightarrow$ Aircraft $\rightarrow$ Equip aircraft. This may seem to be a strange way to group the squad menu, but turns out to offer certain advantages later on. If you followed those instructions you will now see a list off all soldiers available. You can assign soldiers to your dropship by turning the \keybinding{X} buttons to the right of their names into a $\surd$. Clicking on their names brings up their detailed statistics, but instead of doing so we will click the arrow symbol in the very bottom right-hand corner.

Now we have entered the ``equip squad'' screen. While its particular elements will be discussed later in the Geoscape chapter, we will currently limit ourselves to the most urgent actions. First you need to get an overview about your soldiers' weapon skills using the ``actors abilities'' screen. Once you have done so, you should determine many weapons of each kind (assault, heavy etc.) you want to use for your squad, taking into account how many weapons of each class you actually own. If you lack a certain item, you can try to buy the missing ones using the ``Buy / Sell Equipment'' menu (reached through the base screen). After you've done your best to equip every soldier with the best you can get, make sure to hand them all the armor you have, and extra ammunition is always helpful. Now, the most important part is done and your squad eagerly awaits its first mission.

In the meantime, your job as the commander of PHALANX isn't halfway done. In order to fight the alien invaders, your task force will rely on the best technology available. Your research department's job is to offer the best the human mind can invent. Using the research menu, you can can decide what your scientists should focus on next. It may also be a good idea to keep your production facilities busy, for example producing more armour.

Now you should be done with the very basics. Of cause there are a whole lot of features out there waiting to be explored, but this is not the place to spoil all your fun in finding out on your own. Instead you may turn up game speed in Geoscape until the first alien attack offers you the chance to prove that you are worthy of leading PHALANX. Until then, you are dismissed -- commander.

