\section{Troubleshooting}
This section tries to address some known problems and possible workarounds. Nevertheless your first and most up-to-date reference should be the project homepage.\\
Your game console is logged to your UFO:AI userdata dir and is named \gamepath{ufoconsole.log}. It might have some useful information on what is wrong. Make sure that you are also reading our FAQ\footnote{\url{http://ufoai.ninex.info/wiki/index.php/FAQ}}.

\subsection{Turning off sound completly}
Even if this is not an elegant way to solve problems, it at least helps to narrow things sometimes to switch off any sound. While just turning the volume to zero still loads the drivers \consolecommand{+set snd\_init 0} (needs to be entered within the shell / command line on windows) disables them completly. If this solves your problem, please send us an bugreport to help improving the game.

\subsection{Video drivers}
If the game doesn't start up you should make sure, that you've installed the latest vendor specific video hardware drivers for your card - especially on Windows Vista and Linux.

\subsection{Turning on developer mode}
You can set the cvar \cvar{developer} to \cvarvalue{1} or use the \consolecommand{setdeveloper} command to activate the debug output on the game console. \textbf{Warning:} There might be a lot of output that will flood your game console. The output is stored in your \gamepath{ufoconsole.log}.

\subsection{Reset your configuration}
It might also help from time to time to reset your configuration. Delete \gamepath{config.cfg} in your UFO:AI userdata directory to get a fresh restart.
